Datasheet for 'Indicators_of_Anxiety_or_Depression_Based_on_Reported_Frequency_of_Symptoms_During_Last_7_Days_20240401

### 2024-04-19 outputs/paper/datasheet_template.qmd
Update datasheet_template.qmd

---
title: "Datasheet for 'A dataset'"
subtitle: "My subtitle if needed"
author: Chay Park
thanks: "Code and data are available at: LINK."
date: "`r Sys.time()`"
date-format: "D MMMM YYYY"
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

1. *For what purpose was the dataset created? Was there a specific task in mind? Was there a specific gap that needed to be filled? Please provide a description.*
    - The dataset was created to enable analysis of Australian politicians. We were unable to find a publicly available dataset in a structured format that had the biographical and political information on Australian politicians that was needed for modelling.
2. *Who created the dataset (for example, which team, research group) and on behalf of which entity (for example, company, institution, organization)?*
    - TBD
3. *Who funded the creation of the dataset? If there is an associated grant, please provide the name of the grantor and the grant name and number.*
    - TBD
4. *Any other comments?*
    - TBD

@@

	- TBD

@@

	- TBD

@@

	- TBD

@@

	- TBD

@@

	- TBD

@@

	- TBD

@@

	- TBD

@@

	- TBD

@@

	- TBD

@@

	- TBD

@@

	- TBD

@@

	- TBD

@@

	- TBD

@@

	- TBD
16. *Any other comments?*
	- TBD

@@

>>>>

---
title: "Datasheet for 'Indicators_of_Anxiety_or_Depression_Based_on_Reported_Frequency_of_Symptoms_During_Last_7_Days_20240401'"
author: Chay Park
thanks: "Code and data are available at: https://github.com/Chay-HyunminPark/Anxiety_depressive_disorder"
date: "`r Sys.time()`"
date-format: "D MMMM YYYY"
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

1. *For what purpose was the dataset created? Was there a specific task in mind? Was there a specific gap that needed to be filled? Please provide a description.*
    - The dataset was created to complement the ability of the federal statistical system to respond and provide relavant information about how emergent issues are impacting American households (National Center for Health Statistics, 2024). 
2. *Who created the dataset (for example, which team, research group) and on behalf of which entity (for example, company, institution, organization)?*
    - Data was provided by NCHS/DHIS and the owner of the dataset is NCHS.
3. *Who funded the creation of the dataset? If there is an associated grant, please provide the name of the grantor and the grant name and number.*
    - Although there was not significant information specified about the funding, generally in addition to annual appropriations from Congress, NCHS receives additional resources in the form of reimbursables from other Federal agencies. NCHS is reimbursed by other agencies to add specific questions of interest to our surveys (National Center for Health Statistics, 2023). 
4. *Any other comments?*
    - Survey datas that are open to public is scarce and often not open to public. However, regarding health statistics for US research, NCHS is a good place to start with.

@@

	- Online questionnaire based survey with texts only.

@@

	- Just a single survey questionnaire.

@@

	- The dataset contain all possible instances, and yet considered a sample of instances from a larger set as it is still missing some responses from the whole population. The larger set would be a survey response from the whole population in US. The representativeness was verified as the hosting institution is the government associated. 

@@

	- Raw data is nicely formatted in CSV form. Data types are among the following : 'Text', 'Floating Timestamp', and 'Number.' 

@@

	- Columns in this Dataset. (1) Indicator - Data Type [Text] (2) Group - Data Type [Text] (3) State - Data Type [Text] (4) Subgroup - Data Type [Text] (5) Phase - Data Type [Text] (6) Time Period - Data Type [Text] (7) Time Period Label - Data Type [Text] (8) Time Period Start Date - Data Type [Floating Timestamp] (9) Time Period End Date - Data Type [Floating Timestamp] (10) Value - Data Type [Number] (11) Low CI - Data Type [Number] (12) High CI - Data Type [Number] (13) Confidence Interval - Data Type [Text] (14) Quartile Range - Data Type [Text]

@@

	- Column 'Quartile Range' is missing for non-By State group. Only rows with 'By State' group has Quartile Range information.

@@

	- The combination of Symptoms of Depressive Disorder and Symptoms of Anxiety Disorder are combined as Symptoms of Anxiety Disorder or Depressive Disorder. 

@@

	- No

@@

	- Not shown so far.

@@

	- The dataset is self-contained.

@@

	- Dataset could have been labeled White as Caucasian, Black as African American. Also, they are excluding the minorities by grouping them all as 'Non-Hispanic, other races and multiple races.' For instance, South Asian Americans, Middle Eastern Americans, Native Americans. 

@@

	- By age, 18 - 29 years, 30 - 39 years, 40 - 49 years, 50 - 59 years, 60 - 69 years, 70 - 79 years, and 80 years and above. By sex, there are male and female.

@@

	- No, each subgroup population is the accumulated, therefore it's hard to identify single individual.

@@

	- The data reveals race, highest educational attainment, region (states), age.

@@

@online{cdc_nchs_rate,
    title = {Indicators of Anxiety or Depression Based on Reported Frequency of Symptoms During Last 7 Days},
    author = {National Center for Health Statistics},
    year = {2024},
    url = {https://data.cdc.gov/NCHS/Indicators-of-Anxiety-or-Depression-Based-on-Repor/8pt5-q6wp/about_data},
    organization = {National Center for Health Statistics},
    address = {United States},
    note = {Accessed on April 1, 2024},
}
